---
title: "Eating Out"
author: "Cyndhell Anne Pilarca"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction


In this analysis we're gonna identify the difference in each ethnicity about the frequency of eating out. We will find the significance of these each ethnicity in this analysis.


## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```


# Method

Race ~ frequency of eating out

# Results


## Descriptive Results


### Graphical Results
```{r}
barchartGC(~race + eatout,data = mydata)
barchartGC(~race + eatout,data = mydata, type = "percent")
```

These graphs chart suggests that it have a small differences between the ethnicity eating out. 


### Numerical description

```{r}
table1 <- xtabs(~race + eatout, data=mydata)
rowPerc(table1)
colPerc(table1)
```
The result in this numerical description streets and shows the frequency of eating out in white ethnicity as opposed to black and other ethnicity. The table shows white ethnicity frequency of eating out is more than black and other ethnicity.


## Inferential Result

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout, printAll=T)
```

Chi squared result in the p-value is 0.0008179. We see the number is too small that's why we reject the null hypothesis.

# Discussion/Conclusion 

The p-value is so small that's why we reject the null hypothesis based on the result. Therefore, I conclude there is difference in ethnicity based on the frequency they eating out. 





